Dismal Code: Studying the Evolution of Security Bugs

### 2013-09-12 docs/evol.tex
added usenix bib

@@

Completing the above approaches, our work focuses on the subset of security bugs.
Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
the evolution of software defects by examining six major versions of Firefox.
To achieve this they created a database schema that contained information
coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
list,\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
Bugzilla entries and others. Their findings indicated that security bugs are
persistent over time. They also showed that there are many web users that use
old versions of Firefox, meaning that old attacks will continue to work.
Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
security bugs with performance bugs. This was also done by analysing the project's
Bugzilla. Their research presented evidence that security bugs require more experienced developers
to be fixed. In addition, they suggested that security bug fixes are more complex than the
fixes of performance and other bugs.
Shahzad et al.~\cite{SSL12} analysed large sets of vulnerability data-sets to observe
various features of the vulnerabilities that they considered critical. Such features
were the functionality and the criticality of the defects. Their analysis
included the observation of vulnerability disclosures, the behavior of
hackers in releasing exploits for vulnerabilities, patching and others. In
their findings they highlighted the most exploited defects and showed that
the percentage of remotely exploitable vulnerabilities has gradually increased
over the years. Finally, Edwards et al.~\cite{EC12} have recently conducted
a study similar  to ours in which they have considered only four projects.
Their results demonstrate that the number of exploitable bugs does not
always improve with each new release and that the rate of discovery of
exploitable bugs begins to drop three to five years after the
initial release.

>>>>

\author{
% 1st. author
\alignauthor
Dimitris Mitropoulos\\
       \affaddr{Department of Management Science and Technology}\\
       \affaddr{Athens University of Economics and Business}\\
       \email{dimitro@aueb.gr}
% 2nd. author
\alignauthor
Vassilios Karakoidas\\
       \affaddr{Department of Management Science and Technology}\\
       \affaddr{Athens University of Economics and Business}\\
       \email{bkarak@aueb.gr}
% 3rd. author
\alignauthor
Panos Louridas\\
       \affaddr{Department of Management Science and Technology}\\
       \affaddr{Athens University of Economics and Business}\\
       \email{louridas@aueb.gr}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Georgios Gousios\\
       \affaddr{Software Engineering Research Group}\\
       \affaddr{Delft University of Technology}\\
       \email{G.Gousios@tudelft.nl}
% 5th. author
\alignauthor Diomidis Spinellis\\
       \affaddr{Department of Management Science and Technology}\\
       \affaddr{Athens University of Economics and Business}\\
       \email{dds@aueb.gr}
}

@@

Completing the above approaches, our work focuses on the subset of security bugs.
Focusing on such bugs is not a new idea.
Ozment and Schechter~\cite{OS06} examined the code base of the Open{\sc bsd}
operating system to determine whether its security is increasing
over time. In particular, they measured the rate at which new code
has been introduced and the rate at which defects have been reported over
a 7.5 year period and fifteen releases.
Even though the authors present statistical evidence
of a decrease in the rate at which vulnerabilities are being reported
defects seem to appear persistent for a period of at least 2.6 years.
Massacci et al.~\cite{MNN11} observed
the evolution of software defects by examining six major versions of Firefox.
To achieve this they created a database schema that contained information
coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
list,\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
Bugzilla entries and others. Their findings indicated that security bugs are
persistent over time. They also showed that there are many web users that use
old versions of Firefox, meaning that old attacks will continue to work.
Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
security bugs with performance bugs. This was also done by analysing the project's
Bugzilla. Their research presented evidence that security bugs require more experienced developers
to be fixed. In addition, they suggested that security bug fixes are more complex than the
fixes of performance and other bugs.
Shahzad et al.~\cite{SSL12} analysed large sets of vulnerability data-sets to observe
various features of the vulnerabilities that they considered critical. Such features
were the functionality and the criticality of the defects. Their analysis
included the observation of vulnerability disclosures, the behavior of
hackers in releasing exploits for vulnerabilities, patching and others. In
their findings they highlighted the most exploited defects and showed that
the percentage of remotely exploitable vulnerabilities has gradually increased
over the years. Finally, Edwards et al.~\cite{EC12} have recently conducted
a study similar  to ours in which they have considered only four projects.
Their results demonstrate that the number of exploitable bugs does not
always improve with each new release and that the rate of discovery of
exploitable bugs begins to drop three to five years after the
initial release.
